### 2024-09-24 Paper Category/main.tex
New

\end{itemize}
\section*{Holography}
\begin{itemize}
    \item %\cite{Pasterski:2020pdk}
    S.~Pasterski and A.~Puhm,
    ``Shifting spin on the celestial sphere,''
    Phys. Rev. D \textbf{104}, no.8, 086020 (2021)
    doi:10.1103/PhysRevD.104.086020
    [arXiv:2012.15694 [hep-th]].
    69 citations counted in INSPIRE as of 17 Sep 2024\\
    The author aims to  expand the existing framework surrounding conformal primary
    states. They explore conformal primary wavefunctions for all half integer spins up to the graviton within the Celestial Holography program.
    \item %\cite{Crawley:2023brz}
    E.~Crawley, A.~Guevara, E.~Himwich and A.~Strominger,
    ``Self-dual black holes in celestial holography,''
    JHEP \textbf{09}, 109 (2023)
    doi:10.1007/JHEP09(2023)109
    [arXiv:2302.06661 [hep-th]].
    19 citations counted in INSPIRE as of 17 Sep 2024\\
    The author use the celestial holography formalism to construct 2D quantum states for 4D linearized rotating self-dual black holes in (2,2) signature Klein space.
\end{itemize}
\section*{Formal Amplitude Method}
\begin{itemize}
    \item  %\cite{Chen:2023dcx}
    A.~S.~K.~Chen, H.~Elvang and A.~Herderschee,
    ``Bootstrapping the String Kawai-Lewellen-Tye Kernel,''
    Phys. Rev. Lett. \textbf{131}, no.3, 031602 (2023)\\
    doi:10.1103/PhysRevLett.131.031602
    [arXiv:2302.04895 [hep-th]].\\
    15 citations counted in INSPIRE as of 17 Sep 2024\\
    This paper extends the minimal rank KLT bootstrap to 6-point, finding novel restrictions on the 4
    and 5-point double-copy maps.
    \item %\cite{Cristofoli:2022phh}
    A.~Cristofoli, A.~Elkhidir, A.~Ilderton and D.~O'Connell,
    ``Large gauge effects and the structure of amplitudes,''
    JHEP \textbf{06}, 204 (2023)
    doi:10.1007/JHEP06(2023)204
    [arXiv:2211.16438 [hep-th]].
    12 citations counted in INSPIRE as of 17 Sep 2024\\
    The author show that large gauge transformations modify the structure of momentum conservation.
\end{itemize}
\end{document}

>>>>

\section*{Holography}
    \item %\cite{Pasterski:2020pdk}
    S.~Pasterski and A.~Puhm,
    ``Shifting spin on the celestial sphere,''
    Phys. Rev. D \textbf{104}, no.8, 086020 (2021)
    doi:10.1103/PhysRevD.104.086020
    [arXiv:2012.15694 [hep-th]].
    69 citations counted in INSPIRE as of 17 Sep 2024\\
    The author aims to  expand the existing framework surrounding conformal primary
    states. They explore conformal primary wavefunctions for all half integer spins up to the graviton within the Celestial Holography program.
    \item %\cite{Crawley:2023brz}
    E.~Crawley, A.~Guevara, E.~Himwich and A.~Strominger,
    ``Self-dual black holes in celestial holography,''
    JHEP \textbf{09}, 109 (2023)
    doi:10.1007/JHEP09(2023)109
    [arXiv:2302.06661 [hep-th]].
    The author use the celestial holography formalism to construct 2D quantum states for 4D linearized rotating self-dual black holes in (2,2) signature Klein space.
\section*{Formal Amplitude Method}
    \item  %\cite{Chen:2023dcx}
    A.~S.~K.~Chen, H.~Elvang and A.~Herderschee,
    ``Bootstrapping the String Kawai-Lewellen-Tye Kernel,''
    Phys. Rev. Lett. \textbf{131}, no.3, 031602 (2023)\\
    doi:10.1103/PhysRevLett.131.031602
    [arXiv:2302.04895 [hep-th]].\\
    15 citations counted in INSPIRE as of 17 Sep 2024\\
    This paper extends the minimal rank KLT bootstrap to 6-point, finding novel restrictions on the 4
    and 5-point double-copy maps.
    \item %\cite{Cristofoli:2022phh}
    A.~Cristofoli, A.~Elkhidir, A.~Ilderton and D.~O'Connell,
    ``Large gauge effects and the structure of amplitudes,''
    JHEP \textbf{06}, 204 (2023)
    doi:10.1007/JHEP06(2023)204
    [arXiv:2211.16438 [hep-th]].
    12 citations counted in INSPIRE as of 17 Sep 2024\\
    The author show that large gauge transformations modify the structure of momentum conservation.
%\cite{Bern:2019prr}
Z.~Bern, J.~J.~Carrasco, M.~Chiodaroli, H.~Johansson and R.~Roiban,
``The duality between color and kinematics and its applications,''
J. Phys. A \textbf{57}, no.33, 333002 (2024)
doi:10.1088/1751-8121/ad5fd0
[arXiv:1909.01358 [hep-th]].
455 citations counted in INSPIRE as of 23 Sep 2024
\section*{CK duality in curved spacetime}
    \item %\cite{Cheung:2022pdk}
    C.~Cheung, J.~Parra-Martinez and A.~Sivaramakrishnan,
    ``On-shell correlators and color-kinematics duality in curved symmetric spacetimes,''
    JHEP \textbf{05}, 027 (2022)
    doi:10.1007/JHEP05(2022)027
    [arXiv:2201.05147 [hep-th]].
    50 citations counted in INSPIRE as of 23 Sep 2024\\
    The author introduce a isometry frame on symmetric manifold to define a perturbatively calculable quantity—the on-shell correlator, which can be seen as 
    the generalization of on-shell quantity to curved spacetime.
    \item %\cite{Ben-Shahar:2021zww}
    M.~Ben-Shahar and H.~Johansson,
    ``Off-shell color-kinematics duality for Chern-Simons,''
    JHEP \textbf{08}, 035 (2022)
    doi:10.1007/JHEP08(2022)035
    [arXiv:2112.11452 [hep-th]].
    52 citations counted in INSPIRE as of 23 Sep 2024\\
    The author show that 3D Chern-Simons theory obeys off-shell color-kinematics duality and this holds both for gauge field and BRST ghosts.
    \item %\cite{Cheung:2021zvb}
    C.~Cheung and J.~Mangan,
    ``Covariant color-kinematics duality,''
    JHEP \textbf{11}, 069 (2021)
    doi:10.1007/JHEP11(2021)069
    [arXiv:2108.02276 [hep-th]].
    65 citations counted in INSPIRE as of 23 Sep 2024\\
    The author construct an
    explicit implementation of the double copy at the level of fields and equations of motion. They find that YM theory has a so-called "covariant 
    double copy" property and can be related to GR.
    \item %\cite{Chi:2021mio}
    H.~H.~Chi, H.~Elvang, A.~Herderschee, C.~R.~T.~Jones and S.~Paranjape,
    ``Generalizations of the double-copy: the KLT bootstrap,''
    JHEP \textbf{03}, 077 (2022)
    doi:10.1007/JHEP03(2022)077
    [arXiv:2106.12600 [hep-th]].
    50 citations counted in INSPIRE as of 23 Sep 2024\\
    The author formulate a new program to generalize the double-copy of tree amplitudes. They solve the KLT bootstrap equations perturbatively to find the most general higher-derivative
    corrections to the 4- and 5-point field theory KLT kernel.
    \item %\cite{Zhou:2021gnu}
    X.~Zhou,
    ``Double Copy Relation in AdS Space,''
    Phys. Rev. Lett. \textbf{127}, no.14, 141601 (2021)
    doi:10.1103/PhysRevLett.127.141601
    [arXiv:2106.07651 [hep-th]].
    58 citations counted in INSPIRE as of 23 Sep 2024\\
    The author present a double copy relation in Ad$\mathrm{S}_5$ which relates tree-level four-point amplitudes of supergravity, super Yang-Mills and bi-adjoint scalars.
    \item %\cite{Campiglia:2021srh}
    M.~Campiglia and S.~Nagy,
    ``A double copy for asymptotic symmetries in the self-dual sector,''
    JHEP \textbf{03}, 262 (2021)
    doi:10.1007/JHEP03(2021)262
    [arXiv:2102.01680 [hep-th]].
    63 citations counted in INSPIRE as of 23 Sep 2024\\
    The author find an infinite set of double copy constructible symmetries the self-dual sectors
    of Yang-Mills (YM) and gravity, in the light-cone formulation.
    \item %\cite{Albayrak:2020fyp}
    S.~Albayrak, S.~Kharel and D.~Meltzer,
    ``On duality of color and kinematics in (A)dS momentum space,''
    JHEP \textbf{03}, 249 (2021)
    doi:10.1007/JHEP03(2021)249
    [arXiv:2012.10460 [hep-th]].
    80 citations counted in INSPIRE as of 24 Sep 2024\\
    The author explore color-kinematic duality for tree-level AdS/CFT correlators in momentum space, including the integrated correlator and the integrand.
    \item %\cite{Armstrong:2020woi}
    C.~Armstrong, A.~E.~Lipstein and J.~Mei,
    ``Color/kinematics duality in AdS$_{4}$,''
    JHEP \textbf{02}, 194 (2021)
    doi:10.1007/JHEP02(2021)194
    [arXiv:2012.02059 [hep-th]].
    87 citations counted in INSPIRE as of 24 Sep 2024\\
    The author find analogous BCJ relations for Yang-Mills amplitudes in AdS4 and spell out the relation to 3d
    conformal correlators in momentum space, and speculate on the double copy to graviton
    amplitudes in AdS4.
    \item %\cite{Casali:2020vuy}
    E.~Casali and A.~Puhm,
    ``Double Copy for Celestial Amplitudes,''
    Phys. Rev. Lett. \textbf{126}, no.10, 101602 (2021)
    doi:10.1103/PhysRevLett.126.101602
    [arXiv:2007.15027 [hep-th]].
    66 citations counted in INSPIRE as of 24 Sep 2024\\
    The author show that the celestial amplitudes persist the double copy relation by imposing a celestial double copy.

\section*{Gravitational scattering}
\begin{itemize}
    \item %\cite{Saketh:2021sri}
    M.~V.~S.~Saketh, J.~Vines, J.~Steinhoff and A.~Buonanno,
    ``Conservative and radiative dynamics in classical relativistic scattering and bound systems,''
    Phys. Rev. Res. \textbf{4}, no.1, 013127 (2022)
    doi:10.1103/PhysRevResearch.4.013127
    [arXiv:2109.05994 [gr-qc]].
    65 citations counted in INSPIRE as of 23 Sep 2024\\
    The author compute for the first time the changes in linear momentum and the total radiated linear momentum, in the relativistic classical scattering of two
point-charges, at sixth order in the charge. 
\end{itemize}
\section*{Classical double copy}
\begin{itemize}
    \item %\cite{Monteiro:2020plf}
    R.~Monteiro, D.~O'Connell, D.~Peinador Veiga and M.~Sergola,
    ``Classical solutions and their double copy in split signature,''
    JHEP \textbf{05}, 268 (2021)
    doi:10.1007/JHEP05(2021)268
    [arXiv:2012.11190 [hep-th]].
    82 citations counted in INSPIRE as of 24 Sep 2024\\
    The author find a classical interpretation for the three-point amplitude in a split-signature and the double copy
    of them give some implications of Lorentz signature.
    spacetime
    \item %\cite{delaCruz:2020bbn}
    L.~de la Cruz, B.~Maybee, D.~O'Connell and A.~Ross,
    ``Classical Yang-Mills observables from amplitudes,''
    JHEP \textbf{12}, 076 (2020)
    doi:10.1007/JHEP12(2020)076
    [arXiv:2009.03842 [hep-th]].
    73 citations counted in INSPIRE as of 24 Sep 2024\\
    The author study the classical Yang-Mills observables from the perspective of amplitudes, rather than equations of motion.
    \item %\cite{Shi:2021qsb}
    C.~Shi and J.~Plefka,
    ``Classical double copy of worldline quantum field theory,''
    Phys. Rev. D \textbf{105}, no.2, 026007 (2022)
    doi:10.1103/PhysRevD.105.026007
    [arXiv:2109.10345 [hep-th]].
    50 citations counted in INSPIRE as of 23 Sep 2024\\
    The author establish a classical double
    copy relation of WQFT for classical observables (deflection, radiation).
    \item %\cite{Easson:2020esh}
    D.~A.~Easson, C.~Keeler and T.~Manton,
    ``Classical double copy of nonsingular black holes,''
    Phys. Rev. D \textbf{102}, no.8, 086015 (2020)
    doi:10.1103/PhysRevD.102.086015
    [arXiv:2007.16186 [gr-qc]].
    53 citations counted in INSPIRE as of 24 Sep 2024\\
    The author apply the classical double copy procedure to a class of regular, non-singular black hole solutions, 
    called T-dual-de sitter black hole. They also present the connection
    between horizons on the gravity side and electric fields on the gauge theory side of the double copy.
    \item %\cite{Keeler:2020rcv}
    C.~Keeler, T.~Manton and N.~Monga,
    ``From Navier-Stokes to Maxwell via Einstein,''
    JHEP \textbf{08}, 147 (2020)
    doi:10.1007/JHEP08(2020)147
    [arXiv:2005.04242 [hep-th]].
    56 citations counted in INSPIRE as of 24 Sep 2024\\
    The author build the single copy gauge fields which map to fluid-dual metrics, for two different classes of Navier-Stokes solutions.

\end{itemize}
\section*{Twistor method}
\begin{itemize}
    \item %\cite{White:2020sfn}
    C.~D.~White,
    ``Twistorial Foundation for the Classical Double Copy,''
    Phys. Rev. Lett. \textbf{126}, no.6, 061602 (2021)
    doi:10.1103/PhysRevLett.126.061602
    [arXiv:2012.02479 [hep-th]].
    90 citations counted in INSPIRE as of 24 Sep 2024\\
    The author show that a particular incarnation - the Weyl double copy - can be derived using well-established
ideas from twistor theory and answer many questions about double copy.
\end{itemize}
\section*{Kinematics algebra}
\begin{itemize}
    \item %\cite{Chacon:2020fmr}
    E.~Chac\'on, H.~Garc\'\i{}a-Compe\'an, A.~Luna, R.~Monteiro and C.~D.~White,
    ``New heavenly double copies,''
    JHEP \textbf{03}, 247 (2021)
    doi:10.1007/JHEP03(2021)247
    [arXiv:2008.09603 [hep-th]].
    59 citations counted in INSPIRE as of 24 Sep 2024\\
    The author generalize the algebra of self-dual YM by  Moyal deformations, in which case the color-kinematic duality is manifest.
    They also disscuss the classical integrability (or otherwise) of the gauge and gravity theories.
\end{itemize}
\section*{BRST double copy}
\begin{itemize}
    \item %\cite{Borsten:2020zgj}
    L.~Borsten, B.~Jur\v{c}o, H.~Kim, T.~Macrelli, C.~Saemann and M.~Wolf,
    ``Becchi-Rouet-Stora-Tyutin-Lagrangian Double Copy of Yang-Mills Theory,''
    Phys. Rev. Lett. \textbf{126}, no.19, 191601 (2021)
    doi:10.1103/PhysRevLett.126.191601
    [arXiv:2007.13803 [hep-th]].
    63 citations counted in INSPIRE as of 24 Sep 2024\\
    The author show that the double copy of gauge theory amplitudes to N = 0 supergravity amplitudes extends from tree level to loop level.
\end{itemize}
%\cite{Momeni:2020vvr}
A.~Momeni, J.~Rumbutis and A.~J.~Tolley,
``Massive Gravity from Double Copy,''
JHEP \textbf{12}, 030 (2020)
doi:10.1007/JHEP12(2020)030
[arXiv:2004.07853 [hep-th]].
56 citations counted in INSPIRE as of 24 Sep 2024\\
THe author explor the possibility of constructing an interacting massive spin-2 theory, i.e.
massive gravity, as a double copy of massive Yang-Mills theory.

\end{document}
